A Convolutional Neural Network for Outsole Recognition\tnoteref{t1}

### 2019-06-24 paper/paper.Rnw
Consolidate conclusion

% Restate goal
The goal of this research was to develop a method to automatically identify geometric class characteristics of shoe outsoles. Such a method takes the difficult problem of quantifying outsole features in a given population and lays the groundwork for a tractable solution. A set of geometric class characteristics was defined, based on feature sets currently used by examiners, to both broadly classify a large variety of shoes and to narrow down similarity into a manageable number and type of features for further use in a shoeprint analysis. The final set of features used in this research achieves both goals quite well, and has potential for much finer-grained analysis when recognized features are combined with spatial information and relationships.

% Briefly summarize methods
% Overview of results: model generally performs well
The model was developed using the \mt{pre-trained} convolutional base of VGG16 and a newly trained classifier/head to output predicted probabilities within the defined set of geometric features. After training, the model performs well on the data provided. In general, the model is able to identify many well-defined geometric shapes in the images.

>>>>

% Restate goal and briefly summarize methods
The goal of this research was to develop a method to automatically identify geometric class characteristics of shoe outsoles. A set of geometric class characteristics was defined, based on feature sets currently used by examiners, to both broadly classify a large variety of shoes and to narrow down similarity into a manageable number and type of features for further use in a shoeprint analysis. Thousands of outsole images were obtained from online shoe retailers and labeled according to their geometric shapes. A model, the \mt{pre-trained} convolutional base of VGG16 and a newly trained classifier/head, was then trained on a portion of these labeled images to output predicted probabilities within the defined set of geometric features. After training, the model performs well on the data provided. In general, the model is able to identify many well-defined geometric shapes in the images.

%The goal of this research was to develop a method to automatically identify geometric class characteristics of shoe outsoles. Such a method takes the difficult problem of quantifying outsole features in a given population and lays the groundwork for a tractable solution. \mt{Are we alluding to the scanner in this paper, or should I change that to focus on automating what examiners are doing now?} A set of geometric class characteristics was defined, based on feature sets currently used by examiners, to both broadly classify a large variety of shoes and to narrow down similarity into a manageable number and type of features for further use in a shoeprint analysis. \fix{I think our conclusions of overlap make this statement too rosy: The final set of features used in this research achieves both goals quite well, and has potential for much finer-grained analysis when recognized features are combined with spatial information and relationships.}

% Briefly summarize methods
% Overview of results: model generally performs well
%The model was developed using the \mt{pre-trained} convolutional base of VGG16 and a newly trained classifier/head to output predicted probabilities within the defined set of geometric features. After training, the model performs well on the data provided. In general, the model is able to identify many well-defined geometric shapes in the images.
